Manuscript simulations

### 2023-03-02 Manuscript simulations.Rmd
fixed typo

# convenience
`%notin%` <- Negate("%in%")
options(mc.cores = parallel::detectCores())
source("simulations/helpers.R")
```

@@

# k5
compas_data[[4]] <- lapply(
  1:100,
  function(x){
    set.seed(x);
    coords_ <- rbind(
        mvtnorm::rmvnorm(15, compas_params$k5$mu[1,], compas_params$k5$sigma[1]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[2,], compas_params$k5$sigma[2]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[3,], compas_params$k5$sigma[3]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[4,], compas_params$k5$sigma[4]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[5,], compas_params$k5$sigma[5]*diag(2))
      )
    list(
      true_coords = coords_, 
      Y =     compas(
        S = 50, 
        dims = 2,
        am = c(5, 5),
        beta.R = c(1, 1), 
        coords = coords_, 
        n.quanti = 1,
        n.quali = 0.05, 
        add1 = 0.05
      )
    )
  }
)
saveRDS(compas_data, file = "simulations/compas_data.rds")
```

>>>>

# convenience
`%notin%` <- Negate("%in%")
options(mc.cores = parallel::detectCores())
source("simulations_helpers.R")
```

@@

# k5
compas_data[[4]] <- lapply(
  1:100,
  function(x){
    set.seed(x);
    coords_ <- rbind(
        mvtnorm::rmvnorm(15, compas_params$k5$mu[1,], compas_params$k5$sigma[1]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[2,], compas_params$k5$sigma[2]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[3,], compas_params$k5$sigma[3]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[4,], compas_params$k5$sigma[4]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[5,], compas_params$k5$sigma[5]*diag(2))
      )
    list(
      true_coords = coords_, 
      Y =     compas(
        S = 50, 
        dims = 2,
        am = c(5, 5),
        beta.R = c(1, 1), 
        coords = coords_, 
        n.quanti = 1,
        n.quali = 0.05, 
        add1 = 0.05
      )
    )
  }
)
saveRDS(compas_data, file = "simulations_compas_data.rds")
```
